Supplementary Materials

### 2022-12-26 manuscript/supplementary.tex
some noets

Our model is essentially a generalized nonlinear model with a binomial link
function. This is the form used by \textcite{Elyashiv2016-vt} and
\textcite{Murphy2022-sj}. These models fit the observed number of pairwise
nucleotide differences in genomic windows to the expected pairwise diversity
under some evolutionary model. We only consider BGS models here, so the mean
function for position $x$ is the product of the proportion by which BGS reduces
diversity at $x$, $B(x)$, and genome-wide neutral diversity $\pi_0$,

@@

$\Phi$ is the set of BGS parameters (i.e. the DFE for each feature type and
mutation rate), and $\pi_0$ is determined by the drift-effective population
size, set by only reproductive and reproductive processes. Then the ob

fit a nonlinear theoretic equation to
observed count data summarized at some pre-specified scale.

@@

\begin{align}
  n_{D,i} \sim \text{Binom}(\pi_i, n_{T,i})
\end{align}

>>>>

Our model is essentially a generalized nonlinear model with a binomial link
function. This is the form used by \textcite{Elyashiv2016-vt} and
\textcite{Murphy2022-sj}. These models fit the observed number of pairwise
nucleotide differences in genomic windows to the expected pairwise diversity
under some evolutionary model. We only consider BGS models here, so the mean
function for position $x$ is the product of the proportion by which BGS reduces
diversity at position $x$, $B(x)$, and genome-wide neutral diversity $\pi_0$,

@@

$\Phi$ is the set of BGS parameters (i.e. the DFE for each feature type and
mutation rate), and $\pi_0$ is determined by the drift-effective population
size, set by only reproductive and demographic processes.

Our statistical models use a binomial likelihood for the observed data
summarized at some physical genomic scale. The evolutionary processes that
impact $\pi(x)$ do so on different spatial scales, and genomic evolutionary
model selection also includes determining the scale at which data fits best.
The likelihood considers the probability of observing $n_{D,i}$ pairwise
differences in window $i$ given $n_{T,i}$ total possible pairwise comparison,
and that the probability of observing a pairwise difference is given by $\pi_i$

\begin{align}
  n_{D,i} \sim \text{Binom}(\pi_i, n_{T,i}).
\end{align}

This assumes infinite sites, since $\pi_i$ is assumed to be the probability of

Note that this makes the approximation that the average number of pairwise
differences $\pi_x$ is small, such that the probability of heterozygosity
is equal to the

, which links the mean function
above with the probability of observing

sampling process by which individuals are sampled from the population

@@
